Comparative Evaluation of Spark and Flink Stream Processing

### 2017-02-21 paper/paper.tex
added spark impl of sector change detection

\subsection{Evaluation Workloads}
In our experimental evaluation, we developed two streaming processing workloads that read the ADS-B messages stream from Kafka to perform basic trajectories analysis methods. In our design choice, we try to cover key main points related to the streaming processing, to evaluate how  does each framework perform. The following are general key aspects of  streaming data processing were covered by our workloads design:

@@

\subsubsection{Statistics Computation per Trajectory}
In first stream processing workload, we perform statistics calculation for each trajectory (i.e.,  messages of the same ID) in ADS-B messages stream. As example of computed statistics indexes speed mean, mean of location coordinates, min and max altitude, etc. In this workload, we try to cover 
the parallel receiving of input data stream, state-full stream aggregation, and preserve the order of stream records.
The implementation details of this workload in Spark and Flink, are presented in the following: 
\begin{itemize}
\item {\bf{Implementation in Spark }}

@@

//TODO: discuss differences between flink and spark.

@@

\section{Performance Results}

>>>>

\subsection{Evaluation Streaming Workloads}
In our experimental evaluation, we developed two streaming processing workloads that read the ADS-B messages stream from Kafka to perform basic trajectories analysis methods. In our design choice, we try to cover key main points related to the streaming processing, to evaluate how  does each framework perform. The following are general key aspects of  streaming data processing were covered by our workloads design:

@@

\subsubsection{Statistics Computation per Trajectory}
In first stream processing workload, we perform statistics calculation for each trajectory (i.e.,  messages of the same ID) in ADS-B messages stream. As example of computed statistics indexes speed mean, mean of location coordinates, min and max altitude, etc. In this workload, we try to cover 
the parallel receiving of input data stream, state-full stream aggregation, and preserve the order of stream records.
The implementation details of this workload in Spark and Flink are presented in the following: 
\begin{itemize}
\item {\bf{Implementation in Spark }}

@@

//TODO: discuss differences between Flink and Spark.

@@

 The implementation details of this workload in Spark and Flink are presented in the following: 
 \begin{itemize}
 \item {\bf{Implementation in Spark }}

 we implement this workload, based on the following operation stages: 
 \begin{enumerate*}[label={\alph*)}]
 \item receive and build the trajectories stream 
 \item manage the aggregate state and assign the sector for each trajectory.
 \item identify the  change of sector per trajectory if exist
 \end{enumerate*}

 figure 4 shows the Spark streaming APIs used to implement trajectory's sector change detection workload. First, the trajectories stream is built using \texttt{mapToPair}, \texttt{filter}, and \texttt{groupByKey} APIs as was discussed in statistics computation workload. Second,  \texttt{updateStateByKey} API is used to assign corresponding sector for all new aircraft positions in  micro batch  and aggregate last position in previous batch. Finally, the detection of sector change is done by extra filtering transformation using \texttt{filter} API, by identifying the change of sectors in each trajectory.  
 \begin{figure}[h]

      \caption{Spark streaming implementation of sector change detection workload.}
 \end{figure}

 \item {\bf{Implementation in Flink }}
 \end{itemize}
\section{Performance Results}
